Condition-Based Maintenance for Systems based on Bayesian Component Models***

### 2016-10-04 cbm-rbd-paper.tex
ideas for paper structure

>>>>

\section{***summary of ASCE-ASME paper}

sets of priors on component survival,
survival signature,
test data inclusion,
noninformatiove censoring,
set of system reliability curves as output,
wider set in case of prior-data conflict

\section{***extensions to ASCE-ASME paper}

repaired components: separate type in survival signature,
but same hyperparameter learning.

\section{***from (set of) survival curves to maintenance decision}

infinite-horizon cost rate (discounted as well?)
like in age-based policy:
this indicates in how much time from now one should repair the system

\begin{align*}
g(\tau) &= \frac{ECC(\tau)}{ECL(\tau)} = \frac{c_p \Rsys(\tau) + c_u \big(1-\Rsys(\tau)\big)}{\tau \Rsys(\tau) + \int_0^\tau \Rsys(t) \dd t}
\end{align*}

and $\tau^* = \arg\min g(\tau)$ is the cost-optimal repair time from now

sets of $\Rsys(t)$: need to determine sets of $g(\tau)$.
for each $\tau$, fix $\Rsys(\tau) \in [\lRsys(\tau), \uRsys(\tau)]$ and optimize $I(\tau) = \int_0^\tau \Rsys(t) \dd t$:
$\ol{I}(\tau)$ by $\uRsys(t)$, $\ul{I}(\tau)$ by $\lRsys(t)$ until level of $\Rsys(\tau)$.

from sets of $g(\tau)$ to (set of) $\tau^*$:
worst case, best case, interval (how?)
